DraftOne

### 2016-06-02 DraftOne.Rmd
Simulating continuous exposure with seasonal trends

```{r}
# A function for binary exposure which varies by season:
season_binexp <- function(n, p){
  p <- p #Change this later to reflect probability varying by season using trends
  binexp <- sample(c(0,1), size = n, replace = T, prob = c(1-p, p))
  return(binexp)
}
```

@@

```{r}
#Here, exposure would be the output from the season_binexp function and t would be the output from the calc_t function. 
sim_outcome <- function(n, mean_out, t, exposure, rr){
  day <- c(1:n)
  rr <- ifelse(exposure == 1, rr, 1)
  mean_outcome <- mean_out*t*rr
  sim_outcome <- rpois(n, mean_outcome)
  return(sim_outcome)
}
```

@@

```{r}
#Make this function output a dataframe with date, x, etc.
sim_seasdata <- function(n, rr, trend, x_type="binary", p, mean_out){
  if(x_type == "binary"){
    x <- season_binexp(n, p)
  } 
  else if(x_type == "continuous"){

  }
  t <- calc_t(n, trend)
  outcomes <- sim_outcome(n, mean_out, t, x, rr)
  return(outcomes)
}
```

>>>>

```{r}
# A function for binary exposure which varies by season:
season_binexp <- function(n, p){
  p <- p #Change this later to reflect probability varying by season using trends
  binexp <- sample(c(0,1), size = n, replace = T, prob = c(1-p, p))
  return(binexp)
}

# A function for continuous exposure which varies by season:
season_contexp <- function(n, mu, sd, trend){
  day <- c(1:n)
  if (trend=="cos1"){
    mu <- mu*(1+.6*cos(2*pi*(day/365)))
  }
  if (trend == "cos2"){
    mu <- mu*(1+.6*cos(2*pi*(day/365)) + ifelse(day<639 & day>274, .4*cos(2*(pi*(day/365))), 0))
  }
  if (trend == "cos3"){
    mu <- mu*(1+.75^(day/365)*.6*cos(2*pi*(day/365)))
  }
  if (trend == "linear"){
    mu <- mu* (1+ (day/n))
  }
  if (trend == "curvilinear"){
    mu <- mu*(1+day*(2/n)+day^2*(-1/n^2))
  }
  if (trend == "cos1linear"){
    mu <- mu*((1+(day/n)) *(1+.6*cos(2*pi*(day/365))))
  }
  if (trend == "cvd"){ #Figure this out later.
  } #else{
    #stop("Specify a trend variable from cos1, cos2, cos3, linear, curvilinear, cos1linear, or cvd."
    #)}
  contexp <- rnorm(n, mean=mu, sd=sd)
  return(contexp)
}
```

@@

```{r}
#Here, exposure would be the output from the season_binexp function and t would be the output from the calc_t function. 
sim_binout <- function(n, mean_out, t, exposure, rr){
  day <- c(1:n)
  rr <- ifelse(exposure == 1, rr, 1)
  exp_base_y <- mean_out*t
  exp_y <- mean_out*t*rr
  y <- rpois(n, exp_y)
  df <- data.frame(exp_base_y=exp_base_y, exp_y=exp_y, y=y)
  return(df)
}

#Here, exposure would be the output from the season_contexp function and t is from calc_t.
sim_contout<- function(n, mu, t, exposure, rr){
  day <- c(1:n)
  exp_y <- mu*t*rr*(exposure/sd(exposure))
  y <- rpois(n, exp_y)
  df <- data.frame( exp_y=exp_y, y=y)
  return(df)
}
```

@@

```{r}
#Put "date" in the data frame like the others? 
sim_seasdata <- function(n, rr, trend, x_type="binary", p, mu, sd, mean_out){
  if(x_type == "binary"){
    x <- season_binexp(n, p)
    t <- calc_t(n, trend)
    simdata <- data.frame(x, sim_binout(n, mean_out, t, x, rr))
  } 
  else if(x_type == "continuous"){
    x <- season_contexp(n, mu, sd, trend)
    t <- calc_t(n, trend)
    simdata <- sim_contout(n, mu, t, x, rr)
  }
 return(simdata)
}
```
